Collaborative Visual Analysis on the Web with RCloud

### 2015-06-15 discussion.tex
working

Experience with deploying RCloud in a community of data analysts
(``hackers'') gave us some insight into whether the proposed
requirements are appropriate, and how well they were met.

@@

\paragraph*{Shared artifacts and artifact histories} are a central feature of
RCloud, through its shared workbooks of experiments and analyses. We
observed that hackers readily share work through RCloud. They use it to
demonstrate techniques, share results with peers and managers, and to
transfer algorithms to other groups. Artifact histories can be accessed through the notebook
tree or through GitHub's web interface.

\paragraph*{Modularity and granularity} The ability to partition work into
independent units (modularity) is a key to working productively in teams.
It is good if the units can be kept small, so team members can realize
benefits at least proportional to the work on the units (granularity).
RCloud's notebook and versioning capabilities allow work to be divided
into units as fine as the underlying language allows, and versioning
encourages making incremental changes at low cost and without disrupting
the work of others.

\paragraph*{View sharing, bookmarking} Most resources in RCloud are named
and accessed as URLs. This proved to be an effective mechanism for
sharing and for integrating analyses with external processes and systems.
It is particularly advantageous for work to be shared as URLs that
provide access to code and experiments, instead of by pasting static
screenshots into documents and presentations.

>>>>

Experience with deploying RCloud in a community of data analysts
(``hackers'') gave us some insight into whether the proposed
requirements were appropriate, and were met.

@@

\paragraph*{Shared artifacts and artifact histories} are a central feature
of RCloud, through shared workbooks. We observed that hackers readily
share experiments, demonstrate techniques, publish results to peers and
managers, and transfer algorithms to other groups. Artifact histories
can be accessed through the notebook tree or through GitHub's web interface.
But a probem is that it is easy to create a large number of artifacts
and the system does not help enough in their organization and mangement.

\paragraph*{Modularity and granularity} The ability to partition work into
independent units (modularity) is a key to working productively in teams.
It is good if the units can be kept small or granular, so team members can
realize benefits at least proportional to the work on the units.
RCloud's notebook and versioning capabilities allow work to be divided
into units as fine as the underlying language allows, and versioning
encourages making incremental changes at low cost and without disrupting
the work of others.

\paragraph*{View sharing, bookmarking} Most resources in RCloud are named
and accessed as URLs. This proved to be effective for sharing and integrating
analyses externally. It is particularly advantageous for work to be shared
as URLs that provide access to code and experiments, instead of by pasting
screenshots into reports.
